### 2016-11-23 src/4_OnlineLearning.tex
reunion 20 nov

A learning algorithm $\mathcal{A}$ takes as input a data set $S \in \mathcal{S}$ and outputs a function $f$:

\begin{eqnarray*}
\mathcal{A}: \mathcal{S} &\rightarrow & \mathcal{H} \\
S &\rightarrow &\mathcal{A}(S) = f
\end{eqnarray*}

\noindent where $\mathcal{H}$ is called the {\em hypothesis space}, is the space of functions that the algorithm is allowed to search. The selection of $f_S$ is based on the minimization if the expected risk of the loss function $V(f(x),y): \R\times\R\to\R$.

\begin{equation}
\label{eq:expetedrisk}
E[V(f(x),y)] = \int_{X \times Y} V(f(x),y) \, \, dp(x,y)
\end{equation}

@@

@@

\begin{equation} 
\label{eq:erm}
R_{\text{emp}}[f] = \frac{1}{n} \sum_{i=1}^n V(f(x),y)
\end{equation}

>>>>

A learning algorithm $\mathcal{A}$ takes as input a data set $S \in \mathscr{T}=\mathscr{P}(X\times Y)$ and selects from $\mathcal{H}$ a function $f$ such that $f(x)\approx y $ in a predictive way:

\begin{eqnarray*}
\mathcal{A}: \mathscr{T} &\rightarrow & \mathcal{H} \\
S &\rightarrow &\mathcal{A}(S) = f
\end{eqnarray*}

\noindent where $\mathcal{H}$ is called the {\em hypothesis space}, is the space of functions that the algorithm is allowed to search. The selection of $f$ is based on the minimization of the expected error of the loss function $V(f(x),y)$ defined as:

\begin{eqnarray*}
 V(f(\cdot),\cdot): X\times Y &\rightarrow & Y \\
  (x, y) &\rightarrow &V(f(x),y)
\end{eqnarray*}

@@

Given a function $f$ a loss function $V$ and a probability distribution $p$ over $X \times Y$, the expected error of $f$ is:

\begin{equation}
\label{eq:expetedrisk}
E[V(f(\cdot),\cdot)] = \int_{X\times Y} V(f(x),y)\;dp(x,y)\,,
\end{equation}

@@

\begin{equation} 
\label{eq:erm}
R_{\text{emp}}[f] = \frac{1}{n} \sum_{i=1}^n V(f(x_i),y_i)
\end{equation}

The ERM is a Riemann sum approximation of the expected error of $f$ shown in equation \ref{eq:expetedrisk}, where $dp(x,y) \approx 1/n$.
